---
title: "Using_BLBLogistic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using BLBLogistic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This package builds a logistic regression model using R's built-in "glm" function, and retrieves both estimates and intervals of regression coefficients, sigmas, and predictions when applicable. The following is a walkthrough of the package's utilization, using a provided dataset "bank-additional-clean.csv" that is a cleaned version of the dataset found here: https://archive.ics.uci.edu/ml/datasets/bank+marketing.
__Note: Imported dataset cannot include any NA values.__

First we load the package:
```{r setup}
library(BLBLogistic)
```
We build the model using the package's _blbglm_ function, that takes in *five* parameters: 
* 1) _formula_: The formula that we wish to regress the data upon.
* 2) _data_: PATH of the dataset to take in.
* 3) _m_: The number of partitions ("bags") you wish to make in your future bootstrap data (default to 2)
* 4) _B_: The number of bootstrap resamplings you wish to make of each partition in _m_ (default to 10)
* 5) _parallel_: Boolean indicating whether you want to utilize parallelization (for larger datasets) (default to FALSE)
```{r}
bank = read.csv("C:/Users/Alvis/Desktop/bank-additional-clean.csv")
data <- blbglm(y ~ (.), data = bank)
```

We then extract coefficient estimates for each bootstrap in each bag, and generate a mean confidence interval for said estimates.
* NOTE: confint() takes an additional parameter _parm_ to specify which specific estimate CI's you wish to retrieve.
```{r}
coef(data)
confint(data)
```

We can then extract sigma from said estimates, and generate a singular confidence interval for sigma.
```{r}
sigma(data)
```

We generate a probability prediction/prediction interval (if applicable) for each estimate, taking in up to *four* parameters:
* 1) _object_: PATH of the dataset to read.
* 2) _newdata_: An optional data frame of equal length of _object_, to replace fitted values for predicted estimates.
* 3) _confidence_: A boolean operator indicating output of prediction interval (default to FALSE)
* 4) _level_: The quantile of which you wish you prediction to be generated upon (default to 0.95 or 95%)
```{r}
predict(data)
```

